Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-30 02_Paper/paper.tex
more on the trees.

\subsection{Random Forests}
Random Forests \cite{breiman2001random} \MW{Will finish tomorrow.}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Random Forest          & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}

>>>>

\subsection{Decision Tree}
Decision trees are binary trees, these binary trees work with the input
features at the roots, resulting decisions are found by moving
trough the tree to top leaves. At every branch in the tree a decision
is made, until one arrives at the final conclusion \cite{Marsland2015Machine}.
Decision trees are trained using  
\MW{Will write more tomorrow.}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
                Random Forest classification on our annomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}
